\documentclass[12 pt, reqno]{amsart}

\usepackage{../current_style}

\begin{document}

\title{Breaded \& Baked Tofu}
\maketitle
\subtitle{30 minutes plus around 2 $\frac{1}{2}$ hours in marinating and baking}

\noindent \desc{This is a somewhat low effort tofu dish. It requires a little bit of foresight, asking to marinate the tofu for a few hours, but other then that it doesn't ask for a lot. I like this on salads with a thicker dressing, maybe ginger miso, for example. Generally, it's a nice flavor for the tofu and gives a nice crunch to things that otherwise might be lacking.}

\recipe{
\textbf{Marinade}
\begin{ingredients}
  \item Extra Firm Tofu 
  \item $\frac{1}{3}$ cup Soy sauce 
  \item $\frac{1}{4}$ cup Mirin or Rice wine vinegar 
  \item 1 cup water
  \item 2 tsp Garlic Powder 
  \item 2 tsp ground ginger 
  \item 2 tbsp Miso 
  \item 1-2 tbsp Sesame Oil 
\end{ingredients}
\textbf{Breading}
\begin{ingredients}
  \item Red Pepper Flakes or Cayenne pepper 
  \item Nutritional Yeast 
  \item Flour 
  \item garlic powder
  \item cayenne 
  \item salt
  \item sesame oil
\end{ingredients}
}{
\begin{directions}
\item Drain Tofu and dice into half to quarter inch pieces. Combine Soy sauce, Mirin, Miso, Sesame oil, spices, and some water together, it should cover at least half of the tofu. If it doesn't, add more water or scale up the liquids. Add in the spices and marinate the tofu for 1-2 hours, perturbing frequently. 
\item Preheat the oven to 350. Mix all the breading ingredients except sesame oil. Take the tofu out of the marinade and use a spoon to coat with the flour mixture. You might want to reserve the marinade, it could be a good sauce. 
\item Place on rimmed baking sheet with parchment paper and drizzle oil over top. Bake for around 45 minutes---until the tofu bits are golden, shake periodically. Allow to cool.
\end{directions}
}

\end{document}
