\documentclass[12 pt, twoside]{amsart}

\usepackage{../current_style}

\begin{document}



\title{Bagels}
\maketitle
\subtitle{An hour plus 1 $\frac{1}{2}$ hours to rise and about a half hour to bake}

\noindent \desc{I love bagels. This recipe is pretty much verbatim from a friend, but it's pretty much my go-to when making bagels. It takes a long time, so it may be worth doubling the recipe, as it only makes 8 bagels. But when made well, they are really good. Bread flour can be easily replaced with all-purpose flour, but the higher protein flour is appreciated by the bagels.}

\recipe{
\begin{ingredients}
  \item 4 cups bread flour
  \item 2 $\frac{1}{4}$ tsp active dry yeast
  \item 3 tbsp brown sugar
  \item 3 tbsp white sugar
  \item 3 tsp salt
  \item 1 egg
  \item toppings
\end{ingredients}
}{
\begin{directions}
  \item Start by activating the yeast: mix in the active dry yeast with a teaspoon of sugar and 1 $\frac{1}{2}$ cups of warm water. This should sit for about 5 minutes
  \item Meanwhile, mix the flour, salt, and a tablespoon of each sugars together. Then add the activated yeast liquid and knead for five minutes.
  \item Place dough in a generously oiled bowl and cover with a damp cloth. Let rise for 1 $\frac{1}{2}$ hours.
  \item In a large pot place 8 cups of water alongside the remaining two tablespoons of each sugar. Bring to a boil.
  \item While the water boils, punch the dough down, and cut into 8 roughly equal pieces of dough. Roll each into a ball and then punch a hole in the middle. Widen to form a bagel shape.
  \item Preheat the oven to 425 Fahrenheit. Prepare a baking sheet with parchment paper and, if wanted, a place to place wet bagels. Drop as many bagels as comfortably fit into the boiling water. They should rise. Let them boil on one side for a minute before flipping over. Remove them and repeat with the other bagels.
  \item Beat the egg and brush on top of boiled bagels. Immediately sprinkle generously with whatever toppings you want.
  \item Bake for about 20-30 minutes. They should be somewhat hard on the outside and golden. Let cool.
\end{directions}
}

\end{document}
