\documentclass[12 pt, twoside]{amsart}

\usepackage{../current_style}

\begin{document}
\title{Choclate Mixed Berry Tart}
\maketitle
\vspace{-0.75 cm}
\begin{center}
About an hour of work and then four of resting
\end{center}
\vspace{0.375 cm}
Maybe it wouldn't be best to call this a tart, but that's what it is, I guess. It's really just jam under a bunch of chocolate and almost-marzipan. I've used an almond crust here, baked for a half hour and then spread a simple jam before being topped with a mountain of chocolate. I've used coconut milk instead of heavy cream in the ganache. One could easily substitute this for heavy cream, but could also be substituted for silken tofu. This would have to be blended up though, but ends up with a very satisfying result.

\hfill \\

\columnratio{0.4,0.5}
\begin{paracol}{2}	

\large
\noindent \textbf{Ingredients:} \\ \\
\normalsize
\textbf{Almond Crust:}
\begin{itemize}
\item $2$ $1/2$ cups almond flour 
\item $1/2$ tsp salt 
\item 1 egg 
\item 3 Tbsp coconut oil 
\item 2 Tbsp maple syrup
\item 1 tsp almond extract
\end{itemize}
\textbf{Berry Jam:}
\begin{itemize}
\item $2\ 1/2$ cups any berries 
\item 2 cups sugar
\item $1/2$ tsp corn starch
\item $1/4$ cup lemon juice or to taste
\item zest of 1 lemon
\end{itemize}
\textbf{Chocolate Ganache:}
\begin{itemize}
\item 2 cups dark chocolate chips 
\item 2 cups Coconut Milk $^*$see note
\item $1/3$ cup coconut oil 
\item $2$ Tbsp water 
\item $1/2$ tsp or to taste salt 
\item $2$ tsp vanilla extract
\end{itemize}
\textbf{Topping}
\begin{itemize}
\item mixed berries
%\item coconut flakes would be a very good alternative to fruit here
\end{itemize}

\switchcolumn
\noindent \large \textbf{Directions} \\ \normalsize
\begin{enumerate}
\item[1.] Preheat the oven to 375 Farenheit. Make the almond crust by melting the coconut oil and combining all the ingredients together and patting into a pie plate. Once pre-heated, bake for 10 minutes. Then take it out and cover the edges with tin foil to stop them from burning. Bake for another 20 minutes.
\item[2.] While the crust bakes, make the jam. Put all berries in a pot with sugar and cook on medium high. Let mixture boil for around 10 minutes---until beginning to thicken and visibly reduce. Mix in corn starch, lemon juice, and lemon zest. Set aside in the fridge until the crust is done.
\item[3.] Start making the chocolate Ganache: Bring coconut milk to a boil in a sauce pan. Cut the heat and add chocolate, coconut oil, water, and salt. Mix until everything has melted together. Add in vanilla extract.
\item[4.] Once the crust is done, spread the jam in an even layer on the crust. Set aside until the jam begins to gel, around a half hour, placing in a cool area helps.
\item[5.] Once the jam is less liquid, pour in the ganache slowly. Fridge for 4 hours, or until set. Top with berries and serve.
\end{enumerate}
\end{paracol}
*Note: coconut milk can be substituted with heavy cream or blended silken tofu in similar quantities.

\end{document}
