\documentclass[12 pt, twoside]{amsart}

\usepackage{../current_style}

\begin{document}
\title{Gingerbread Cake}
\maketitle
\vspace{-0.75 cm}
\begin{center}
    An hour and a half plus cooling and assembling
\end{center}
\vspace{0.375 cm}
Adapted from \href{https://www.youtube.com/watch?v=YUgz7Kx7eJU}{America's Test Kitchen}. Makes a very rich four-layer gingerbread cake with a dairy-free frosting. The cake batter before baking will seem very liquid, if you can't resist adding more dry ingredients, you can probably get away with a quarter or half cup of flour more, but it should work out very well if you stick with it.

\hfill \\
\columnratio{0.4,0.5}
\begin{paracol}{2}	

\large
\noindent \textbf{Ingredients:} \\ 
\normalsize
\textbf{Cake}
\begin{itemize}
\item 2 cups all purpose flour
\item 3/2 tsp baking powder
\item 3/4 tsp salt
\item 2 tbsp powdered ginger
\item 1 tsp cinnamon
\item 1/2 tsp white pepper
\item 1/8 tsp cayenne pepper
\item 1/4 cup cocoa powder
\item 3/4 cup molasses
\item 1 cup brewed coffee
\item 1/2 tsp baking soda
\item 3/4 cup vegetable oil
\item 1 1/4 cup sugar
\item 3 eggs
\item 2 tbsp grated fresh ginger
\end{itemize}
\textbf{Vanilla Custard Frosting}
\begin{itemize}
\item 750 mL oat milk
\item 150 g sugar
\item 55 g cornstarch
\item 250 g coconut oil
\item 1 tbsp apple cider vinegar
\item 1 tbsp lemon juice
\item 2 tbsp orange juice
\item 1/2 tsp nutritional yeast
\item 4 drops orange essential oil
\item 1 tbsp vanilla
\end{itemize}


\switchcolumn
\noindent\large\textbf{Directions} \\ \normalsize
\begin{enumerate}
\item[1.] Preheat the oven to 350 farenheit. In a medium bowl, mix flour, baking powder, and salt. Then add powdered ginger, cinnamon, white pepper, cayenne pepper, and cocoa powder.
\item[2.] In a separate bowl, mix together molasses and coffee. Then add the baking soda, vegetable oil, sugar, eggs, and grated ginger. Mix and add to the dry ingredients. 
\item[3.] Pour 1 1/3 cups of the batter into two 8" cake pans and bake for 12-14 minutes or until a toothpick inserted comes out clean. Cool for 10 minutes, remove from the pan, and repeat.
\item[4.] While the cakes bake, start with the custard frosting. In a pot, heat the oat milk and sugar until hot, reserving 50 mL of oatmilk. Slowly stir cornstarch into the reserved oat milk and add to the pot. You may need to blend the mixture if the oat milk or cornstarch clumps
\item[5.] Cut the heat and add coconut oil, vinegar, lemon juice, and orange juice. Add these slowly and to taste, you don't want to overpower the frosting, they should bring it a bit closer to a cream cheese taste while giving it some citrus. End with the orange essential oil and vanilla. Cool until jelly or overnight.
\item[6.] Stack each individual cake with a healthy portion of frosting in between. End with a crumb coat and garnish as you like.
\end{enumerate}
\end{paracol}
\end{document}
