\documentclass[12 pt, twoside]{amsart}

\usepackage{../current_style}

\begin{document}
\title{Granola}
\maketitle
\vspace{-0.75 cm}
\begin{center}
    An hour to prep, two to rest, and two to bake.
\end{center}
\vspace{0.375 cm}
I love granola, it's kind of the perfect snack. You can have it whenever, and with so many things, if it doesn't turn out good, it's a nice cereal alongside fruit, and you can make it essentially however you want. I usually like to make it somewhat light on the oats and go heavy on nuts, coconut flakes, and other ingredients to add bulk. A favorite combination of mine is hazelnuts and almonds with chocolate or just go all in with almonds and coconut. This recipe is best with many baking sheets to press down the granola, but this step may be skipped if you grind up more oats up front. Also, all the measurements are nowhere near precise, everything can be changed.

\hfill \\
\columnratio{0.4,0.5}
\begin{paracol}{2}	

\large
\noindent \textbf{Ingredients:} \\\normalsize
\begin{itemize}
\item 120 mL / 1/2 cup of oil 
\item 120 grams / 1/2 cup maple syrup
\item 120 grams / 1/2 cup brown sugar 
\item 3/2 tsp salt 
\item 120 mL / 1/2 cup milk
\item your favorite extract/flavoring
\item 450 grams / 5 cups of oats
\item 170+ grams / 2+ cups of nuts (mix and match different kinds if you want) \\
\item 50 grams / 1 cup of coconut flakes 
\item 95 grams / 2/3 cup pumpkin seeds
\item 70 grams / 1/2 cup sunflower seeds
\item 80 grams / 1/3 cup chia seeds
\item 2 tbsp of your favorite spices. Some of mine are Cardamom, Nutmeg, Cinnamon, Clove, Ginger, and Star Anise
\item 60 grams / 1/2 cup cocoa powder
\item Dried fruit
\item Chocolate chips
\end{itemize}

\switchcolumn
\noindent\large \textbf{Directions} \\
\normalsize
\begin{enumerate}
\item[1.] Over heat place oil, maple syrup, brown sugar, and salt. Heat until everything is dissolved, then pour in milk, cook for a few minutes and then let cool. 
\item[2.] Blend up 90 g / 1 cup of oats into a flour and chop the nuts well. Combine as many of the dry ingredients as you like.
\item[3.] Add your favorite extract to the liquid and mix the two together.
\item[4.] Let rest for an hour. Then preheat the oven to 300 farenheit and spread granola onto a baking sheet lined with parchment paper. This should be reasonably thin, this will take many batches. Place another piece of parchment paper on top of the granola and weight down with anything heavy you have. This will help form the granola into clusters.
\item[5.] Bake for an hour or until the bottoms look like they are cooked (this might be harder if you put cocoa powder in, but taste buds are never a bad indicator of done-ness, you are looking for dry and crunchy granola). While this bakes, if you have more baking sheets, prepare the next sheet of granola.
\item[6.] Take out of oven and set aside for an hour or until hardened. If you want, place chocolate to melt on top while still hot. 
\end{enumerate}
\end{paracol}
\end{document}
