\documentclass[12pt, twoside]{amsart}    

\usepackage{../current_style}

\begin{document}

\title{Mixed Street Corn Salad}
\maketitle
\vspace{-0.75 cm}
\begin{center}
10-30 minutes
\end{center}
\vspace{0.375 cm}
This was originally a mishmash of a street corn salad recipe we found from the internet and the various vegetables left in the fridge after a fourth of July celebration. It turned out very well and I decided to write it down. Originally we didn't bake the corn, and it worked very well, cutting down the prep time significantly. Also, the jalapeño peppers could easily be swapped out for chili in adobo for a spicier salad.

\hfill \\
\columnratio{0.4, 0.5}
\begin{paracol}{2}
\large
\noindent \textbf{Ingredients:} \\ \normalsize
\noindent \textbf{Salad}
\begin{itemize}
\item 2 ears of corn
\item 2 cups hearty greens (eg kale, arugala, etc.); regular greens work as well
\item 1/2 a cucumber
\item 1 cup of tomatoes
\item 1/2 cup feta cheese
\item 8 oz cooked chickpeas
\item 1-2 jalapeño peppers*
\item $\frac{1}{4}$ cup chopped cilantro
\item $\frac{1}{4}$ cup chopped basil
\end{itemize}
\hfill \\

\noindent \textbf{Dressing}
\begin{itemize}
\item 2 cloves garlic
\item juice \& zest of 1 lime
\item 2-3 Tbsp apple cider vinegar
\item 1 Tbsp mayonaise
\item 2 tsp nutritional yeast
\item 1/2 tsp smoked paprika $^*$see note
\item1/4 tsp salt, or to taste
\end{itemize}

\switchcolumn
\noindent \large \textbf{Directions} \\ \normalsize

\begin{enumerate}
\item[1.] Shuck the corn and place it in the oven. Preheat the oven to 350, once it's at heat, cook for 20 minutes.
\item[2.] Deflaming the garlic: finely mince the garlic, put it in a bowl with the lime juice and zest and apple cider vinegar. 
\item[3.] While waiting for the corn, combine the rest of the ingredients in the salad.
\item[4.] Add the mayonnaise to a small bowl, add all the dressing ingredients including the garlic and the lime juice. 
\item[5.] When the corn is done, slice the kernels of corn from the cob. Combine with the rest of the salad.
\item[6.] Mix dressing into the salad and serve.
\end{enumerate}
\begin{adjustwidth}{20pt}{0pt}
\noindent *Note: The Jalapeño peppers and smoked paprika could be replaced by some chili in adobo---about 1-3 tsp---and a bell pepper for a spicier salad.
\end{adjustwidth}

\end{paracol}

\end{document}
