\documentclass[12pt, twoside]{amsart}    

\usepackage{../current_style}

\begin{document}

\title{Soup Base}
\maketitle
\vspace{-0.75 cm}
\begin{center}
45 minutes to an hour
\end{center}
\vspace{0.375 cm}
This is a basic base I use for most soups, it might get changed on a per-recipe basis, but this is how I start most things. I've listed a few veggies---carrots, peppers, celeries, mushrooms (ok not a vegetable)---really these could be anything that cooks well. Fennel is a favorite in my family, as are jalapeños, but this is just to give the soup a nice base. 


\hfill \\
\columnratio{0.4, 0.5}
\begin{paracol}{2}
\large
\noindent \textbf{Ingredients:} \\ \normalsize
\begin{itemize}
\item 2 medium onions
\item 2 large carrots
\item 2 bell peppers
\item 1 stalk of celery
\item mushrooms
\item 1/2 to 1 cup of wine of choice OR
\item a few tablespoons of vinegar of choice
\item 3 cloves of garlic
\item 6 cups of vegetable stock or water with bouillon
\item 1-2 tbsp each of thyme, rosemary, oregano
\item 2 tsp each red pepper flakes, coriander, garlic/onion powder, anything more that fits
\item 1 bay leaf
\end{itemize}


\switchcolumn
\noindent \large \textbf{Directions} \\ \normalsize

\begin{enumerate}
\item[1.] Finely dice onions and sauté in oil and salt while you cut up the rest of the rest of the veggies. Once all of them are cut up and the onions are starting to become translucent (10 minutes) add the rest of the veggies with a bit more salt and let cook for another 20 minutes.*
\item[2.] Once beginning to gain color and lose shape, add wine or vinegar; if using vinegar dilute with water; let cook uncovered for 15 minutes. Mince or grate garlic and make a spot for them to cook, add a little bit more oil as necessary. Once they brown, incorporate them with the rest of the veggies.
\item[3.] Add the liquid and spices and proceed with making the soup.
\end{enumerate}
\begin{adjustwidth}{20pt}{0pt}
I've listed only a few vegetables here, really whatever veggies you have in your fridge that sauté will be good.
\end{adjustwidth}
\end{paracol}

\end{document}