\documentclass[12 pt, twoside]{amsart}

\usepackage{../current_style}

\begin{document}
\title{``Any way Puy Lentils''}
\maketitle
\vspace{-0.75 cm}
\begin{center}
45 minutes to an hour
\end{center}
\vspace{0.375 cm}
This was originally from Anna jones' \textit{Easy Wins}, it's the recipe of the same name. I've changed it a little bit and added some more spices. I cook it frequently enough that I thought it would be worth including. The idea is to create two separate dishes, one being a pretty sweet and bright tomato sauce, and the other being a darker lentil dish, and then serve them together with a little bit of yogurt or sour cream. I'll say this with most things, but you can certainly add more veggies (to the lentils in this cse), it just makes the dish better.

\hfill \\
\columnratio{0.4, 0.5}
\begin{paracol}{2}
\noindent \large \textbf{Ingredients:} \normalsize \\
\textbf{Lentils}
\begin{itemize}
\item 1 onion
\item 1 large carrot
\item 1 bell pepper
\item 1 garlic clove
\item 2 tsp each rosemary and thyme
\item Vegetable bullion or vegetable stock
\item 1 cup of green puy lentils
\item red wine vinegar
\end{itemize}

\textbf{Tomato Sauce:}
\begin{itemize}
\item 1 onion
\item 1 carrot
\item 2 garlic cloves
\item 1 16oz can of tomatoes
\item 2 tsp each basil and oregano
\end{itemize}


\switchcolumn
\large \textbf{Directions} \normalsize \\
\begin{enumerate}
\item[1.] Start with the lentils. Dice and sauté both onion over medium heat with salt. While that cooks, dice the carrot and pepper. After ten minutes, remove half the onion and set aside, ideally on another medium burner. Then add in the other vegetables. Let cook for twenty minutes.
\item[2.] Add in the garlic, either diced or grated, and cook just until it browns. Then add in the rest of the ingredients and cook for twenty minutes, and then uncovered until most of the liquid has evaporated and the lentils are a good consistency.
\item[3.] While the lentils cook, continue cooking the other half of the onion. While it cooks, grate the carrot into the onion for sweetness. Once you are done grating the carrot and the onions are starting to become mushy, add the garlic as you did the previous clove.
\item[4.] After the garlic is done, add the tomatoes and spices, salt to taste, and cook over medium low until the lentils are done.
\item[5.] Keep the two dishes separate until you serve. Serve topped with sour cream.
\end{enumerate}
\end{paracol}


\end{document}
